Evaluation of the locality of the Mainline DHT

### 2014-05-29 paper.tex
updated paper

Figure \ref{fig:exp1,1-ids1-cache0} shows an steady average of 6 hops, a value very close to the network mean 7.5. This is because nodes perform queries to random buckets, and because we have an average of less than one node per bucket $26/160$, there is no chance for the routing policy to perform any kind of selection based on RTT measurements.

>>>>

Figure \ref{fig:exp1,1-ids1-cache0} shows an steady average of 6 hops, a value very close to the network mean 7.5. This is because nodes perform queries to random buckets, and because we have an average of less than one node per bucket $26/160$, there is little chance for the routing policy to perform selection based on RTT measurements, only the farthest buckets from each node ID has several competing routing nodes.
